Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-10 PAPER.tex
fairly complete draft minus jackknive section and cocnlusion

We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter. Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and $\hat{\textbf{C}} = \hat{\textbf{C}} * \textbf{I}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}. All three are in agreement, validating our analytical thermal noise calculation.

@@

Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}. The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \hat{\textbf{C}}*\textbf{I}$, in order to minimize signal loss. We show upper limits ($2\sigma$ error bars) for three different results. Our revised error estimation method is in black, where we only bootstrap along the baseline axis and we maximize sensitivity by random sampling only the last baseline in each group. The red curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group. In blue, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data. We under-estimate errors in doing so because we are drawing many more samples than independent ones.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used, where $\hat{\textbf{C}}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss. Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly). The blue result bootstraps over both the baseline and time axes, and illustrates how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
	\label{fig:data_errors}
\end{figure}

>>>>

We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter. Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}. All three are in agreement, validating our analytical thermal noise calculation.

@@

Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}. The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$ in order to minimize signal loss. We show upper limits ($2\sigma$ error bars) for three different results. Our revised error estimation method is in black, where we only bootstrap along the baseline axis and we maximize sensitivity by random sampling only the last baseline in each group. The red curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group. In blue, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data. We under-estimate errors in doing so because we are drawing many more samples than independent ones.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/data_errors.png}
	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used in order to minimize signal loss. Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly). The blue result bootstraps over both the baseline and time axes, and illustrates how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
	\label{fig:data_errors}
\end{figure}
